%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{iftex}
\usepackage{fontspec}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\ifPDFTeX
  \input{glyphtounicode}
\fi
\usepackage{fontawesome5}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\setmainfont[
  Path=fonts/,
  UprightFont=Geist-Regular.ttf,
  BoldFont=Geist-Regular.ttf,
  ItalicFont=Geist-Regular.ttf,
  BoldItalicFont=Geist-Regular.ttf,
  BoldFeatures={FakeBold=1.6},
  ItalicFeatures={FakeSlant=0.2},
  BoldItalicFeatures={FakeBold=1.6,FakeSlant=0.2}
]{Geist}
\setsansfont[
  Path=fonts/,
  UprightFont=Geist-Regular.ttf,
  BoldFont=Geist-Regular.ttf,
  ItalicFont=Geist-Regular.ttf,
  BoldItalicFont=Geist-Regular.ttf,
  BoldFeatures={FakeBold=1.6},
  ItalicFeatures={FakeSlant=0.2},
  BoldItalicFeatures={FakeBold=1.6,FakeSlant=0.2}
]{Geist}
\setmonofont[
  Path=fonts/,
  UprightFont=Geist-Regular.ttf
]{Geist}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDFs remain machine readable when using pdfLaTeX.
\ifPDFTeX
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Huge Jan Jiménez Serra} & \large {\normalsize \faGlobe}\ \href{https://janjs.dev}{\underline{janjs.dev}} \\
\end{tabular*}
\vspace{6pt}

\noindent
\begin{tabular*}{\textwidth}{@{}c@{\extracolsep{\fill}}c@{}}
  \footnotesize
  \faGithub\ \href{https://github.com/janjs}{\underline{github.com/janjs}}
  \hspace{0.5em} $|$ \hspace{0.5em}
  \faPhone\ +34 684 22 55 70
  \hspace{0.5em} $|$ \hspace{0.5em}
  \faEnvelope\ \href{mailto:jan.jime.serra@gmail.com}{\underline{jan.jime.serra@gmail.com}}
  \hspace{0.5em} $|$ \hspace{0.5em}
  \faMapMarker\ Netherlands (Originally from Barcelona) \\
\end{tabular*}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AI Software Engineer}{October 2021 -- Present}
      {Accenture Netherlands}{Amsterdam (Netherlands)}
      \resumeItemListStart
      \resumeItem{Promoted twice while growing into AI-focused engineering roles spanning LLM platforms, agentic systems, and enterprise AI products.}
      \resumeItem{\textit{German Industrial Machinery} (2026 -- Present): Built Next.js-based agentic systems using LLMs, RAG, and enterprise integrations.}
      \resumeItem{\textit{US Medtech} (2023 -- 2025): Built an internal AI chatbot platform used daily by 50,000+ employees, using Azure OpenAI and AWS Bedrock with enterprise workflows, context-aware agents, and no-code tools for citizen developers.}
      \resumeItem{\textit{Large Dutch Bank} (2021 -- 2023): Helped replace a 20+ year legacy user account platform with Kotlin, Spring, AngularJS, Azure SQL, and Cosmos DB, building backend services serving 1,000+ QPS with $>$99.9\% availability and single-digit millisecond API latency.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Full-stack Software Engineer}{April 2018 -- Dec. 2019}
      {NexoTech}{Mataró, Barcelona (Spain)}
      \resumeItemListStart
        \resumeItem{Led project about designing and building of a full-stack web application build in ReactJS and Java Spring for counting the amount of people in a building with IoT and Deep Learning implementations.}
        \resumeItem{Implemented a Machine Learning model with Keras and Python that recognizes gender and age. Used AWS Rekognition in production for better speed and accuracy.}
      \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {M.Sc. in Computer Science}{Sep. 2020 -- Oct. 2021}
      {Trinity College Dublin}{Dublin, Ireland}
      \resumeItemListStart
        \resumeItem{Specialized in AR/VR, Machine Learning, and Computer Graphics.}
      \resumeItemListEnd
    \resumeSubheading
      {Bachelor’s in Computer Engineering and Information Systems}{Sep. 2016 -- Dec. 2019}
      {Universitat Pompeu Fabra}{Barcelona, Spain}
      \resumeItemListStart
        \resumeItem{Studied a semester abroad at \emph{Ajou University} in Suwon, South Korea.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
      
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{3D Copy \& Paste} $|$ \emph{ARKit, Swift, Python, Blender}}{April 2021 - September 2021}
          \resumeItemListStart
            \resumeItem{Developed an iOS app that obtains a 3D mesh using LiDAR from a 4th Gen iPad Pro, and seamlessly sends the mesh to a 3D modeling program (Blender) by pointing the camera to it.}
            \resumeItem{Blender Add-on written in Python that retrieves the model and positions it at the centroid between the camera picture and the computer screen.}
          \resumeItemListEnd

          More Web and Mobile applications in an abundance of programming language, frameworks and libraries can be found at: \vspace{1pt}
    \href{https://github.com/janjs}{\underline{github.com/janjs}}
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{
      \textbf{Programming Languages}: \textbf{Java} · \textbf{Kotlin} · \textbf{Python} · \textbf{JavaScript/TypeScript}. \\
      \textbf{Frameworks}: React JS · Angular JS · Spring · Three JS · React Native · Django · ARKit · iOS UIKit · OpenGL. \\
      \textbf{Machine Learning}: PyTorch · AWS/GCP machine learning tools (Rekognition, Firebase ML). \\
      \textbf{Database Management}: SQL (MySQL/Oracle/PostgreSQL) · NoSQL (CosmosDB) · Firebase. \\
      \textbf{Developer Tools}: Git · IntelliJ · VS Code · Firebase · XCode · Azure DevOps. \\
      \textbf{Web Markup Languages}: HTML/CSS. \\
      \textbf{Others}: DevOps · OOP · AOP · Computer Graphics (C++) · Machine Learning.
    }
    \item \small{ \textbf{Spoken Languages}: English (\emph{Level C1 - Cambridge English: Advanced}) · Spanish (\emph{Native}) · Catalan (\emph{Native}). }
 \end{itemize}


%-------------------------------------------
\end{document}
